When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
with plots

INSERT FIGURE 1 HERE
<!--
```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}

@@

  #include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))

>>>>

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}

@@

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
